Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
start cut down biolog

>>>>

<!-- 
TODO: cut down to this

Given recent technological advancements in biologging and wildlife tracking technology 
[@Borger_2020], remotely sensed data provides a unique opportunity to use
multilayer social network analysis to answer complex questions about animal
socioecology

track the fine-scale movements of groups over large distances and time scales
[@Torney_2018]
-->
